### 2015-04-21 paper.tex
Discuss wake figures

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel
massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit
amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo
eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla
erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

@@

@@

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}

>>>>

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker.

@@

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicated that the RM2 blades are operating further from
stall---consistent with the higher tip speed ratio operation.

@@

Totals for the transport terms in the mean kinetic energy equation---analyzed
identically to \cite{Bachant2015-JoT}---are shown in Fig.~\ref{fig:Ktransport}.
Due to the weaker blade vortex shedding, we see transport due to vertical
advection at this point in the wake is approximately 3 times lower than the
higher solidity UNH-RVAT. We also see relatively lower levels of cross-stream
turbulent transport thanks to the lack of blade stall vortex shedding. These
results may have interesting implications regarding the application of turbines
with lower power coefficient to possibly improve overall array performance
through enhanced transport of kinetic energy from the free stream, though a
detailed anaylsis of the downstream evolution and turbine interaction will be
necessary.

\begin{figure}[ht!]
%\includegraphics[width=\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}
